Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-03 paper/paper.qmd
Update discussion part, modified structure, added limitation section

Yet, as with all models, limitations persist. While our weighting
system, with its emphasis on recent data, aims to capture a timely
snapshot of voter sentiment, it may miss sudden changes sparked by
campaign events or unexpected shifts in public discourse. The
variability in our state projections—ranging from a low estimate of 363
electoral votes for Harris to a high of 471—reflects the inherent
uncertainty in polling-based models, particularly given the constraints
of our data sources. This wide range suggests that while data-driven
insights can illuminate trends, they cannot fully account for the
unpredictable nature of electoral outcomes. Moving forward,
incorporating real-time sentiment from social media or
demographic-specific insights could offer a more responsive
understanding of voter behavior. Ultimately, these findings highlight
the intricate dance between popular sentiment and the electoral
mechanics of American democracy—a system where every vote counts, but
some states matter just a bit more than others.

## Second discussion point

>>>>

Ultimately, these findings highlight the intricate dance between popular
sentiment and the electoral mechanics of American democracy—a system where
every vote counts, but some states matter just a bit more than others.

## Limitations of the Dataset and Model

Yet, as with all models, limitations persist. While our weighting
system, with its emphasis on recent data, aims to capture a timely
snapshot of voter sentiment, it may miss sudden changes sparked by
campaign events or unexpected shifts in public discourse. The
variability in our state projections—ranging from a low estimate of 363
electoral votes for Harris to a high of 471—reflects the inherent
uncertainty in polling-based models, particularly given the constraints
of our data sources. This wide range suggests that while data-driven
insights can illuminate trends, they cannot fully account for the
unpredictable nature of electoral outcomes. While the dataset provides
an overall approval rating for Harris, it lacks a breakdown by factors
such as age, gender, income, and education, which are critical to
understanding the preferences of different groups of voters. Without
them, our analysis may have overlooked significant changes in specific
groups that could affect overall trends.
